\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\bullet$}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Eddie Wu} \\ \vspace{1pt}
    \small \href{mailto:emwu@uchicago.edu}{\underline{emwu@uchicago.edu}} $|$
    \href{https://www.linkedin.com/in/edward-minghao-wu/}{\underline{LinkedIn}} $|$
    \href{https://github.com/ewu47}{\underline{GitHub}} $|$
    \href{https://eddiemwu.com}{\underline{eddiemwu.com}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Chicago}{Chicago, IL}
      {B.S. Computer Science, B.A. Statistics $|$ GPA: 3.6/4.0}{Sep 2024 -- Jun 2028}
      \resumeItemListStart
        \resumeItem{\textbf{Financial Markets Program:} Selective three-year program focused on quantitative finance acumen through
experiential workshops, mentorship, and coursework at Chicago Booth.}
        \resumeItem{\textbf{Involvement}: Maroon Capital (Analyst), Sports Analytics Group (WebMaster), Maroon Capital Ventures
(Associate Partner), Algo Group, Kappa Theta Pi Tech Fraternity, College IT (Part-Time Computer Assistant)}
        \resumeItem{\textbf{Relevant Coursework:} Theory of Algorithms, Databases, Systems Programming, Discrete Mathematics, Numerical Linear Algebra, Applied Regression Analysis, Computer Science I \& II }
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SAS}{Cary, NC}
      {Software Developer Intern --- Flow Team}{May 2026 -- Aug 2026}
      \resumeItemListStart
        \resumeItem{Built and shipped diagram grid features for data flows in SAS Data and AI Studio within an agile/scrum environment.}
        \resumeItem{Implemented gridline, snap-to-grid, and alignment guide logic in \textbf{React}/\textbf{TypeScript} using the \textbf{GoJS} diagram library.}
        \resumeItem{Refactored diagram utilities into a reusable \textbf{TypeScript} component library, removing redundant logic across the codebase.}
        \resumeItem{Built Jest unit tests covering UI logic across all modified components, achieving \textbf{90\%+} coverage within a CI/CD pipeline.}
      \resumeItemListEnd

    \resumeSubheading
      {MergeWorks}{Remote}
      {AI Agent Fellow (Part-Time)}{Apr 2026 -- Jul 2026}
      \resumeItemListStart
        \resumeItem{Built a production AI agent pipeline with n8n orchestration, GPT-4.1 function calling, and Google Sheets as a data layer.}
        \resumeItem{Engaged in weekly cohort meetings covering tool use, multi-agent orchestration, structured outputs, and HITL patterns}
        \resumeItem{Fully engineered and built the UI dashboard that clients can interact with utilizing n8n webhooks for realtime inventory. }
        \resumeItem{Delivered an end-to-end AI Human-in-the-loop inventory system for clients reducing manual labor time by \textbf{75\%}.}
      \resumeItemListEnd

    \resumeSubheading
      {North Carolina Football Club}{Cary, NC}
      {Data Analyst (Part-Time)}{Jul 2025 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Cut coaching staff manual reporting time by 80\% via weekly \textbf{Plotly}/\textbf{ggplot2} dashboards; pipeline remains in production.}
        \resumeItem{Built a \textbf{PostgreSQL} database centralizing performance metrics for 25+ professional athletes across training and matches.}
        \resumeItem{Ingested 30,000+ StatSports GPS entries in \textbf{Python}/\textbf{R}, surfacing load and recovery trends for coaching decisions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Make Twenty Four} $|$ \emph{React, TypeScript, Vite, Supabase, Tailwind CSS}}{\textit{Apr 2026 -- Present}}
          \resumeItemListStart
            \resumeItem{Designed and built a full-stack real-time math puzzle game (solo, timed, 1v1) with ELO ratings and friend challenges.}
            \resumeItem{Engineered a custom \textbf{TypeScript} game engine: recursive solver, seeded puzzle generation, undo logic, and multiple modes.}
            \resumeItem{Implemented live 1v1 multiplayer via \textbf{Supabase Realtime}: ELO matchmaking, room codes, score sync, and reconnects.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Swarm Wallet} $|$ \emph{TypeScript, React, Node.js} $|$
          \emph{Top 3 Inference Track --- Uncommon Hacks}}{\textit{May 2026}}
          \resumeItemListStart
            \resumeItem{AI shopping platform launching parallel browser agents across 6 live retailers, reducing price-ranked search time by 60\%.}
            \resumeItem{Orchestrated multi-agent pipeline with \textbf{Stagehand} for structured data extraction; streamed agent status via \textbf{WebSocket}.}
            \resumeItem{Integrated \textbf{Snowflake} for persistent search memory: price history and semantic routing from past queries.}
            \resumeItem{Integrated \textbf{Wafer} inference API to serve open-source LLMs across agents, cutting inference cost vs. proprietary APIs.}

          \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Pulse} $|$ \emph{Rust, React, TypeScript, Tauri, Docker}}{\textit{Jan 2026 -- April 2026}}
        \resumeItemListStart
          \resumeItem{Built a cross-platform menu bar app with \textbf{Tauri} (\textbf{Rust} + React/TypeScript) for focus session management.}
          \resumeItem{Engineered a \textbf{Rust} state machine handling focus cycle automation, timer persistence, and window state synchronization.}
          \resumeItem{Implemented system-level app/website blocking and macOS notification suppression via native OS APIs.}
          \resumeItem{Built a \textbf{GitHub Actions} CI pipeline using \textbf{Docker Buildx} with layer caching to cross-compile Tauri/Rust to Linux.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership \& Activities}
  \resumeSubHeadingListStart
      \resumeSubheading
      {University of Chicago Sports Analytics Group}{Chicago, IL}
      {Webmaster}{Dec 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Solely developed the official organization website with 400+ page visits built with \textbf{TypeScript}/\textbf{React}, deployed on Vercel.}
      \resumeItemListEnd
    \resumeSubheading
      {University of Chicago Varsity Men's Soccer}{Chicago, IL}
      {NCAA DIII Student-Athlete $|$ All-American 4th Team, All-Region 1st Team, All-Conference 1st Team}{Aug 2024 -- Present}
      \resumeItemListStart
        \resumeItem{One of $\sim$50 DIII players nationally to earn All-American honors while committing 25+ hrs/week to training and competition alongside full coursework.}
        \resumeItem{Serve on team leadership council and Order of the C representative; help coordinate student-athlete initiatives.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, TypeScript, JavaScript, SQL, R, C, HTML/CSS} \\
     \textbf{Frameworks \& Tools}{: React, Next.js, Node.js, Tauri, n8n, Browserbase, Stagehand, Pandas, NumPy, Docker, Git, AWS} \\
     \textbf{Databases}{: PostgreSQL, Supabase, Snowflake, MongoDB} \\
     \textbf{AI/ML}{: HuggingFace Transformers, PyTorch, scikit-learn, RAG, Claude/OpenAI APIs} \\
     \textbf{Interests}{: Music Production, Chess, Video Editing}
    }}
 \end{itemize}

\end{document}